---
title: "Violent words in news articles"
output: html_document
---

Here, we visualize and analyze the percentage of violent words occurring in different types of news articles. Our hypothesis is that articles about presidential debates show a similar percentage to articles about violent events such as the Syrian War and Hurricane Sandy, but higher ratios than more neutral articles covering the California Drought or the Nobel Peace Prize. 

The plot below shows the percentage for each individual article, grouped by type:

```{r, echo = FALSE,message=FALSE}
# loading necessary libraries
library(mongolite)
library(ggplot2)
library(pander)
library(dplyr)
library(broom)
library(stargazer)
```

```{r, echo = FALSE,message=FALSE, results='hide'}
# getting data out of mongo data base

# articles covering comparison topics
c = mongo(collection = "articles", db = "politics")
df1 = c$find('{}','{"violent_ratio": 1, "topic": 1, "candidate_ratio": 1}')
names(df1)[2] = "article"

# articles about presidental debates
c = mongo(collection = "debates2", db = "politics")
df2 = c$find('{}','{"violent_ratio": 1, "debate": 1, "candidate_ratio": 1}')
df2$debate = paste0("Debate ",df2$debate)
#df2$debate = "Debates"
names(df2)[2] = "article"

# articles covering comparison topics
#c = mongo(collection = "brown", db = "politics")
#df3 = c$find('{"category": "news"}','{"violent_ratio": 1}')
#df3$article = "Brown Corpus"

# combine the dataframes into one
df = rbind(df1, df2)
df$article = as.factor(df$article)
# reorder factors
#df$article = factor(df$article, levels = c("Debates", "Hurricane Sandy", "Syrian War","Drought", "Nobel Peace Prize", "General Election"))
df$article = factor(df$article, levels = c("Debate 1","Debate 2", "Debate 3", "Hurricane Sandy", "Syrian War","Drought", "Nobel Peace Prize", "General Election"))
df$violent_ratio = df$violent_ratio * 100
df$candidate_ratio = df$candidate_ratio * 100

df = filter(df, article != "General Election")
droplevels(df)
```


```{r,echo=FALSE, fig.width=12, fig.height=6}
gp = ggplot(df, aes(x = 1, y = violent_ratio)) + 
  geom_point(size = 3, 
             position = position_jitter(width = .1, height = 0)) 
gp  + 
  geom_errorbar(stat = "hline", yintercept = "mean",
               aes(ymax=..y..,ymin=..y..),
               width = 0.5, col = "black") +
  facet_grid(~article ) +
  ylab("Percentage of violent words") +
scale_x_continuous(breaks=NULL, name="") # + ggtitle("Percentage of violent words across different types of news articles")

```

```{r, echo = FALSE,message=FALSE}

bla = df %>%
  group_by(article) %>%
  summarise(m = mean(violent_ratio), sd = sd(violent_ratio), n = n())
panderOptions("round", 3)
pander(bla)
```


Let's do some stats: Linear Regression with Debate 1 as control level:

```{r, echo = FALSE}
df$group = NA
# df[df$article %in% c("Debate 1","Debate 2", "Debate 3"),]$group = "Debate"
# df[df$article %in% c("Drought", "Nobel Peace Prize"),]$group = "Violent"
# df[df$article %in% c("Hurricane Sandy", "Syrian War"),]$group = "Non-Violent"
# df %>% group_by(group) %>% summarise(m=mean(violent_ratio))

mod = lm(violent_ratio ~ article, df)
panderOptions("round", 5)
tidied = tidy(mod)
tidied$term[1] = "articleDebate 1 (Intercept)"
tidied$term = unlist(lapply(tidied$term, function(x) substring(x, 8)))

pander(tidied, split.table = Inf)
```

```{r, echo=FALSE, results='asis'}
library(stargazer)
stargazer(mod, type = 'html')
```
