---
title: "Visualizing the survey data"
output:
  html_document: default
  word_document:
    reference_docx: apa_styles.docx
---

```{r, echo = FALSE,message=FALSE}

# loading necessary libraries
library(readxl)
library(ggplot2)
library(pander)
library(tidyr)
library(dplyr)
library(knitr)
```
`r opts_chunk$set(echo=FALSE)`

```{r, echo=FALSE}
#setwd("~/Documents/Programming/Polisci-Violence/Results")
survey = read_excel("Debate_Metaphor_Final11.29.xlsx")
# detach("package:reshape")

survey = survey %>%
  gather(condition, value, StrongV:ControlV) %>%
  filter(value == 1) %>%
  select(-value)
levels(survey$condition) = c("Strong Violence","Weak Violence","No Violence")
```
Here is an overview of the questions:
```{r, echo=FALSE}
txt ='
Q1 "Who won last night’s debate"
Q2 "How confident are you about this?"
Q3 "According to the polls, how much of a lead did the Candidate (you selected) have after the debate?"
Q4 "Who receives more votes on election day?"
Q5 "How confident are you about this?"
Q6 "How many votes does the winner receive (than the loser)?"
Q7 "What do you think Candidate A’s political affiliation is?"
Q9 "Who would you vote for?"
'
questions = read.delim(textConnection(txt), sep = " ", header = FALSE) 
names(questions) = c("code", "text")
pander(questions, justify = c('center', 'left'), split.cells = c("10%", "90%"))
```

## Who won the debate?

Let's start with Question 1 and 2, who the winner of the debate was:


```{r}
x=survey %>% 
  group_by(condition, Q1) %>% 
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  select(-n) 
panderOptions("round",3)
y = x %>% 
  spread(condition, freq) %>%
  select(Candidate = Q1,`No Violence`, `Weak Violence`, `Strong Violence`) 
pander(y)
```

The more violent language, the clearer the winner. In control condition, basically 50/50.

```{r, echo=FALSE, message=FALSE, fig.width=10, fig.height=3}
library(likert)
library(reshape)

x = survey[survey$Q1 == 1,] %>% select(Q2)
x$Q2 = as.factor(x$Q2)
x = as.data.frame(x)
lik = likert(x, grouping = survey[survey$Q1 == 1,]$condition)
plot(lik, legend.position = "right") +  theme(text=element_text(size=16, family="Arial")) + ggtitle("Confidence Rating for Q1") 
```

Also more confidence in violent conditions.

We can also try to weigh the votes (see Fausey&Matlock paper). TO BE DONE

## Lead of selected candidate at polls

```{r, echo=FALSE, message=FALSE, fig.width=10, fig.height=3}
library(likert)
library(reshape)

x =  survey[survey$Q1 == 1,] %>% select(3) 
x$Q3 = as.factor(x$Q3)
x = as.data.frame(x)
lik = likert(x, grouping = survey[survey$Q1 == 1,]$condition)
plot(lik, legend.position = "right") +  theme(text=element_text(size=16, family="Arial"))
```

## Election: Who wins the election by how many votes?

Same result as with debate (to be expected). More violence leads to more Candidate 1 selections.

```{r}
x=survey %>% 
  group_by(condition, Q4) %>% 
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  select(-n) 
panderOptions("round",3)
y = x %>% 
  spread(condition, freq) %>%
  select(Candidate = Q4, `No Violence`, `Weak Violence`, `Strong Violence`) 
pander(y)
```

Confidence?

```{r, echo=FALSE, message=FALSE, fig.width=10, fig.height=3}
x = select(survey, Q5)
x$Q5 = as.factor(x$Q5)
x = as.data.frame(x)
lik = likert(x, grouping = survey$condition)
plot(lik, legend.position = "right") +  theme(text=element_text(size=16, family="Arial"))
```

Margin of victory:

```{r, echo=FALSE, message=FALSE, fig.width=10, fig.height=3}
x = select(survey, Q6)
x$Q6 = as.factor(x$Q6)
x = as.data.frame(x)
lik = likert(x, grouping = survey$condition)
plot(lik, legend.position = "right")+  theme(text=element_text(size=16, family="Arial"))
```

## Political Affiliation

What political affiliation does Candidate A have:

```{r, echo=FALSE, message=FALSE, fig.width=10, fig.height=3}
x = select(survey, Q7)
x$Q7 = as.factor(x$Q7)
x = as.data.frame(x)
lik = likert(x, grouping = survey$condition)
plot(lik, legend.position = "right") +  theme(text=element_text(size=16, family="Arial"))
```


## Who would you vote for

```{r}
x=survey %>% 
  group_by(condition, Q9) %>% 
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  select(-n) 
panderOptions("round",3)
y = x %>% 
  spread(condition, freq) %>%
  select(Candidate = Q9, `No Violence`, `Weak Violence`, `Strong Violence`) 
pander(y)


```
```{r, echo=FALSE, message=FALSE, fig.width=10, fig.height=3}
x = select(survey, Q9)
x$Q9 = as.factor(x$Q9)
x = as.data.frame(x)
lik = likert(x, grouping = survey$condition)
plot(lik, legend.position = "right") + ggtitle("Who would you vote for?") 
```

